Refinements for open automata

### 2022-07-08 2021-Refinement/paper/refinementarticle.tex
figures

\begin{figure}[h]
 \centering
   \includegraphics[width=.5\textwidth]{Figures/counter.pdf}\hfill 
   \includegraphics[width=.3\textwidth]{Figures/compose_count_db.pdf}
   \caption{Open Automaton of \texttt{counter} process (left).  Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart. And Open Automation of  the composition \texttt{database}[\texttt{counter/cnt}] (right).\label{Fig:counter}}
\end{figure}
\paragraph{Relations between open automata}
A relation (bisimulation, refinement, etc.) between OA requires to compare their states. To do so we will suppose that the variables of the two OA are disjoint (a renaming of variables may have to be applied before comparing OA states).
\begin{definition}[Relation on OA states] Suppose $V_1$ and $V_2$ are disjoint.
A relation on states of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
\end{definition}
The idea is that two states are related if the variables they refer to verify a certain formula. Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{022} \vdash R\mpar{s_{01}, s_{02}}\).

@@

@@

\begin{center}
\includegraphics[scale=0.7]{Figures/Theorem2}
\end{center}

@@

\subsection{Example}

@@

>>>>

\begin{figure}[h]
 \centering
   \includegraphics[width=.5\textwidth]{Figures/counter.pdf}\hfill 
   \includegraphics[width=.3\textwidth]{Figures/compose_count_db.pdf}
   \caption{Open Automaton of \texttt{counter} process (left).  Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart. And Open Automaton of  the composition \texttt{database}[\texttt{counter/cnt}] (right).\label{Fig:counter}}
\end{figure}
In Fig. \ref{Fig:counter} (right) we present the composition \texttt{database}[\texttt{counter/cnt}] of the two open automata \texttt{database} and \texttt{counter}. Each state of the composite consists of a state of \texttt{database} together with a state of \texttt{counter}. The composed automaton  takes over  the same steps as the   \texttt{database} automaton but it also includes new steps,  indicting the change of states for the setting of timer.

\paragraph{Relations between open automata}
A relation (bisimulation, refinement, etc.) between OA requires to compare their states. To do so we will suppose that the variables of the two OA are disjoint (a renaming of variables may have to be applied before comparing OA states).
\begin{definition}[Relation on OA states] Suppose $V_1$ and $V_2$ are disjoint.
A relation on states of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
\end{definition}
The idea is that two states are related if the variables they refer to verify a certain formula. Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{022} \vdash R\mpar{s_{01}, s_{02}}\).

@@

\begin{figure}[h]
 \centering
   \includegraphics[width=.6\textwidth]{Figures/composeRefined.pdf}
   \caption{The refined Open Automaton composed with the counter \label{Fig:ComposeRefine}}
\end{figure}

@@

\begin{center}
\includegraphics[scale=0.7]{Figures/Theorem2bis}
\end{center}

@@

@@

\section{Example}
